---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# clovers

<!-- badges: start -->
<!-- badges: end -->

The clovers package implements Fader and Hardie's Shifted Beta Geometric model for LTV in a discrete-time, contractual business.

## Installation

The clovers package can be installed from GitHub as follows:

``` {r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("warnerbros/clovers")
```

Once this package is available on CRAN, it can be installed as follows:

``` {r, eval=FALSE}
install.packages("clovers")
```

## Example

This is a basic example:

```{r example}
library(clovers)
```

The package comes with simulated customer-level data:
```{r}
data(customer_lifetimes)
head(customer_lifetimes)
```

Aggregate the customer-level data to the format required by the fitting function:
```{r}
agg_data = transform_individual(customer_lifetimes)
print(agg_data)
```

Fit the model to the aggregated data and print the resulting fit parameters:
```{r}
fit = fit_sbg(agg_data)
print(fit)
```

Display the modeled mean lifetime:
```{r}
lifetime_stats(fit)
```

Plot the modeled distribution of churn rates:
```{r churn_distribution}
plot_churn_distribution(fit, type="count")$plot
```

Draw a plot comparing the modeled survival function to an empirical survival function computed with the Kaplan-Meier estimator:
```{r model_fit}
plot_model_fit(fit, agg_data)$plot
```
